Proof part 1: 3 layers

### 2023-10-04 No Diamond for 3 layers.tex
PROOF

\documentclass[]{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\ReLU}{\mathrm{ReLU}}

@@

@@

\begin{theorem}
	If for all $(a,d)$ there is no compensation paths $(\pi,\pi')$ 
	in the network from $a$ to $d$, then the LP approximation is 
	$100\%$ accurate (or deepoly with the $f(x) \geq 0$ abstraction only, never using the 
	$f(x) \geq x$ abstraction). 
\end{theorem}

\begin{proof}
First we consider the case when there are only three layers: input layer, one hidden layer, and output layer. For convenience, we assume that the output only has one node. Of course, we assume all active functions are ReLU function.

We use $c_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the hidden layer and use $x$ to denote the output node. We use $W$ to denote the weights and $W_{bc}$ and $W_{xb}$ to denote the components. We use capital letter $B$ to denote bias, although it is not important here.

\begin{definition}
	1. We use $b$ to denote the node before ReLU and $\hat{b}$ to denote the node after ReLU: $\hat{b} = \ReLU(b)$.

	2. $\bar{f}$ is the upper bound approximation function of DeepPoly, and $\underline{f}$ is the lower bound approximation function.
\end{definition}

\begin{theorem}
	If there following conditions holds, then the bounds of $x$ obtained by DeepPoly are equal to the actual bounds:

	1. All DeepPoly triangle are right-angled triangle: for any ReLU node $b$ that upper bound $u(b)>0$ and lower bound $l(b)<0$, the approximation of lower bound is the zero function $\underline{f}(b)=0$.

	2. No Diamond: for any input node $c$, any output node $x$, any two paths $p_1,p_2$ from $c$ to $x$ along the direction of forward propagation. If $p_1$ is $c,b_i,x$, $p_2$ is $c,b_j,x$, then for $W_{b_jc}W_{xb_j}$ and $W_{b_ic}W_{xb_i}$, either one of them is $0$, or they have the same sign: both positive or negative.
\end{theorem}

\subsection*{One} First, we compute the bounds obtained by DeepPoly. Without loss of generality, we only consider the upper bound of $x$.   By the algorithm, the DeepPoly upper bound of $x$ is computed by following steps: \begin{align}
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(b_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(b_i)+B_x\\
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+B_x\\
 =& C+\sum_{W_{xb_i}<0}W_{xb_i}\cdot\underline{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\cdot\bar{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)\\
 =& C+\sum_{c_j}c_j\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\\
 \rightarrow& C+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i<0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot l(c_j)\\
 &+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i>0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot u(c_j)
\end{align} Here, $\bar{k_i}$ is the coefficient of $\bar{f_i}$, which is a linear function, and $\underline{k_i}$ is the coefficient of $\underline{f_i}$, which is also a linear function. $C$ is the sum of all constants that occurs in above computations. $K_i$ is the coefficient $\bar{k_i}$ or $\underline{k_i}$ depending on $i$. Notice that by the definition of DeepPoly, all $K_i$ are non negative.

>>>>

\documentclass[]{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\ReLU}{\mathrm{ReLU}}

@@

All DNNs $N$ considered only use ReLU activation function, and are fully connected (some wheight between neurons can be 0 though).
A path $\pi$ in $N$ is a sequence of neurons $(a_i)_{i=0}^n$ such that for all $i < n$, layer($a_{i+1}$) = 1 + layer($a_{i}$).

@@

\begin{theorem}
	If for all $(a,c)$ there is no compensation paths $(\pi,\pi')$ 
	in the network from $a$ to $c$, then the LP approximation is 
	$100\%$ accurate (or DeepPoly with the $f(x) \geq 0$ abstraction only, never using the 
	$f(x) \geq x$ abstraction). 
\end{theorem}

\begin{proof}

	First we consider the case when there are only three layers: input layer, one hidden layer, and output layer.

%We use $c_i$ to denote nodes in the input layer, use $b_j$ to denote nodes in the hidden layer and use $x$ to denote the output node. 
%We use $W$ to denote the weights and $W_{bc}$ and $W_{xb}$ to denote the components. We use capital letter $B$ to denote bias, although it is not important here.

\begin{itemize}
    \item We will denote by $a_i$ nodes in the input layer, and by $b_i$ nodes in the hidden layer.

	\item We use $x^-$ to denote a node before applying the ReLU activation function (but after the linear weighted sum) and $x^+$ to denote the node after applying the ReLU: $x^+ = \ReLU(x^-)$.

	\item We denote by $\bar{f}(x)$ the upper bound approximation function of DeepPoly (using the $f(x) \geq 0$ abstraction only) for node $x$, 
	and $\underline{f}(x)$ its lower bound approximation function.
\end{itemize}

We want to show that for any $c$ in the output layer (3rd layer), there exist 
input $\bar{Y}$ such that $W_{\bar{Y}}(x) = \bar{f}(c)(\bar{Y}) = \min_Y \bar{f}(c)(Y)$, and 
 $\underline{Y}$ such that $W_{\underline{Y}}(x) = \underline{f}(c)(\underline{Y}) = \min_Y \underline{f}(c)(Y)$.

Let $c$ be any output node.

\paragraph{DeepPoly bounds}

First, we compute the bounds obtained by DeepPoly.
The case of the lower bound is symetrical (because the abstraction $f(x)\geq 0$ is used, ensuring that the lower bound of $f(x)$ is reached at 0).

The DeepPoly upper bound of $x$ can be expressed by the following steps:

\begin{align}
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(b_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(b_i)+B_x\\
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+B_x\\
 =& C+\sum_{W_{xb_i}<0}W_{xb_i}\cdot\underline{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\cdot\bar{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)\\
 =& C+\sum_{c_j}c_j\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\\
 \rightarrow& C+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i<0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot l(c_j)\\
 &+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i>0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot u(c_j)
\end{align}

Here, $\bar{k_i}$ is the coefficient of $\bar{f_i}$, which is a linear function, and $\underline{k_i}$ is the coefficient of $\underline{f_i}$, which is also a linear function. $C$ is the sum of all constants that occurs in above computations. $K_i$ is the coefficient $\bar{k_i}$ or $\underline{k_i}$ depending on $i$. Notice that by the definition of DeepPoly, all $K_i$ are non negative.
